---
title: "dev_history.Rmd for RMIS data package"
author: "Ben Cox"
date: "23/01/2021"
output: html_document
---

```{r development, include=FALSE}
library(testthat)
```

<!--
# Description of your package
This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 

```{r description}
# Describe your package
fusen::fill_description(
  fields = list(
    Title = "Download CWT release or recovery data from RMIS",
    Description = "Use Rmd First method to build your package. Start your package with documentation. Everything can be set from a Rmd file in your project.",
    `Authors@R` = c(
      person("Ben", "Cox", email = "benjamin.cox@dfw.wa.gov", role = c("aut", "cre"))
    )
  ),
  overwrite=TRUE
)
# Define License with use_*_license()
usethis::use_mit_license("Ben Cox")
```

```{r function-1}


```

```{r examples}

```

```{r tests}
test_that("my_median works properly and show error if needed", {
  expect_true(my_median(1:12) == 6.5)
  expect_error(my_median("text"))
})
```


```{r function-1}

```

```{r examples-1}

```

```{r tests-1}
```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory

